A Horrocks-type theorem for even orthogonal $K_2$

### 2019-09-28 dl-paper.tex
Fix 5.20

\begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
\begin{proof} Follows from the above lemma and the fact that the generators of $Z_{\alpha,\beta}$ are generators of type 2 for $P_\beta(0)$ in the sense of~\cref{defP0}.
 Indeed, if $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ is such that $\langle \beta, \gamma \rangle = -1$, then $ \langle \alpha - \beta, \gamma \rangle \geq 2$, hence
  $\gamma = \alpha - \beta$, a contradiction. \end{proof}

>>>>

\begin{corollary} The image of $K(\alpha, \beta)$ under $S_\alpha(a, -)$ is contained in $P_\beta(0)$. \end{corollary}
\begin{proof} 
By the above lemma it suffices to show that $Z_{\alpha, \beta} \subseteq P_\beta(0)$.
Let $g = x_{\gamma}(f, X\xi)$ be a generator of $Z_{\alpha, \beta}$.
Notice that $\gamma \in Z_+(\alpha) \setminus \{\alpha - \beta \}$ cannot form an obtuse angle with $\beta$, otherwise from $\langle \beta, \gamma \rangle = -1$ it follows that $ \langle \alpha - \beta, \gamma \rangle \geq 2$ and hence $\gamma = \alpha - \beta$, a contradiction.

If $\langle \beta, \gamma \rangle$ is $0$ or $1$, then $g$ is a generator of type 2 or 3 for $P_\beta(0)$ in the sense of~\cref{defP0}. Finally, $g = z_\beta(f, X\xi)$ also belongs to $P_\beta(0)$ (this follows e.\,g. from Remarks~\ref{Pstar-char}--\ref{rem:palpha}). \end{proof}
